SNARL:\\Simulating Known Actors with Machine Learning

### 2017-05-15 tex/paper/paper.tex
Add Future Work.

Though we have shown that there is significant differentiation between user's typing patterns.

@@

\pagebreak
\printbibliography

>>>>

We have shown that there is significant differentiation between user's typing patterns, as evidenced by the results of our distinguisher model. However, it is not clear to the authors that there exists sufficient entropy in this data to uniquely identify a user in a large system. Certainly, timing delays and key hold times do not render a model that should be used as a second factor alone. We would like to explore how the signal from such a model can be used a heuristic for other biometric factors, as well as whether or not such signals could be aggregated to provide a secure authenication system.

@@

\printbibliography
